\chapter*{Foreword}
\addcontentsline{toc}{chapter}{Foreword}
\markboth{FOREWORD}{FOREWORD}

The \texttt{prismAId} user manual is designed to help researchers, academics, and professionals leverage the power of the \texttt{prismAId} toolkit for conducting systematic reviews efficiently.\reminder{No coding skills are required to effectively conduct a systematic review with \texttt{prismAId}.} This document provides a structured approach to installing, configuring, and using the various components of \texttt{prismAId}, ensuring that users can quickly get started while also exploring advanced features when needed.

This manual is divided into five distinct parts, each catering to different user needs:

\begin{itemize}
    \item \textbf{Part 1: Introduction}\tip{The many open science advantages of \texttt{prismAId} are introduced and discussed in the \secref{chap:intro}{\textbf{Introduction}}.} -- If you are new to \texttt{prismAId}, we recommend starting with the chapter \secref{chap:intro}{\textbf{Introduction to prismAId}}. This section explains what \texttt{prismAId} is, the modular tools it provides, who can benefit from them, and why it is a valuable toolkit for systematic reviews.

    \item \textbf{Part 2: Getting Started}\note{\texttt{prismAId} is available on all platforms and operating systems. It can also be integrated programmatically with the most widely used scientific software.} -- If you need to install and configure \texttt{prismAId}, go directly to \secref{chap:install}{\textbf{Installation \& Setup}}. This section provides step-by-step installation instructions for Windows, Mac, and Linux.

    \item \textbf{Part 3: Conducting a Systematic Review}\tip{For a quick but complete walkthrough on using \texttt{prismAId} in a systematic review, see the \secref{chap:walkthrough}{\textbf{fifth}} chapter.} -- If your primary goal is to \textbf{learn how to conduct a systematic review with \texttt{prismAId}}, you can skip the installation and configuration sections and go directly to the chapter \secref{chap:walkthrough}{\textbf{Step-by-Step Guide to Conducting a Systematic Review}}. This section provides a hands-on walkthrough of:
    \begin{itemize}
        \item Setting up a project
        \item Acquiring and preparing literature using the Download and Convert tools
        \item Configuring and running systematic reviews using the Review tool
        \item Interpreting results
        \item Exporting findings
    \end{itemize}
    Before diving into this walkthrough, you may find it helpful to read \secref{chap:sysrev}{\textbf{Understanding Systematic Reviews}}, which provides background information on the methodology and best practices.

    \item \textbf{Part 4: Advanced Features} -- Users who want to explore advanced capabilities can refer to the chapters \secref{chap:advanced_ensemble}{\textbf{Ensemble Reviews}} and \secref{chap:advanced_features}{\textbf{Debugging, Cost Management \& Integration}}. These sections cover advanced options such as ensemble reviews, rate limiting, cost minimization, and integration with external tools and workflows.

    \item \textbf{Part 5: Troubleshooting \& FAQs} -- If you encounter issues, visit \secref{chap:troubleshooting}{\textbf{Troubleshooting Common Issues}}, which provides solutions to common errors for each of the toolkit's components, and \secref{chap:faq}{\textbf{Frequently Asked Questions}}, which addresses common concerns about usage and implementation.
\end{itemize}

\section*{How Should You Use This Manual?}
\addcontentsline{toc}{section}{How Should You Use This Manual?}

\begin{itemize}
    \item If you are \textbf{new to \texttt{prismAId}}, start with \secref{chap:intro}{\textbf{Introduction}}, then proceed to \secref{chap:install}{\textbf{Installation}}.
    \item If you \textbf{want to conduct a complete systematic review}, go directly to \textbf{Part 3}, particularly \secref{chap:walkthrough}{\textbf{Step-by-Step Guide to Conducting a Systematic Review}}, for a detailed walkthrough of the entire process.
    \item If you only need \textbf{specific tools} from the toolkit (Download, Convert, or Review), the respective chapters in \textbf{Part 3} detail how to use each component independently.
    \item If you need \textbf{advanced features or troubleshooting}, refer to \textbf{Parts 4 and 5} as needed.
\end{itemize}

Throughout this manual, useful commands are presented in blue boxes, as shown below:

\begin{commandbox}[Command: Example of a Binary Command]
To run a systematic review with a TOML configuration file:
\begin{lstlisting}[language=Bash]
# For Windows
./prismaid.exe -project your_project.toml

# For downloading papers from Zotero
./prismaid.exe -download-zotero zotero_config.toml

# For converting PDF files to text
./prismaid.exe -convert-pdf ./papers
\end{lstlisting}
\end{commandbox}

Tool configuration details are highlighted in red boxes, as shown below:

\begin{configbox}[Configuration: Example of a TOML Setting]
To configure an LLM for your review:
\begin{lstlisting}[language=TOML]
# Sample TOML configuration
[project.llm.1]
provider = "OpenAI"
api_key = ""
model = ""
temperature = 0.2
tpm_limit = 0
rpm_limit = 0
\end{lstlisting}
\end{configbox}


\section*{Final Notes}
\addcontentsline{toc}{section}{Final Notes}

We hope this manual serves as a comprehensive guide to making the most of the \texttt{prismAId} toolkit\warning{The online documentation of \texttt{prismAId} is available at \href{https://open-and-sustainable.github.io/prismaid/}{open-and-sustainable.github.io/prismaid/}.}. Whether you're a first-time user or an advanced researcher, this document is structured to help you get the information you need quickly and efficiently. The modular design of \texttt{prismAId} allows you to use only the components you need, making it adaptable to various research workflows and requirements.

This manual provides a complete overview of the features available in \texttt{prismAId} version ≥ 0.8.0. However, many aspects also apply to earlier versions that offer the same features.

For any additional questions, please refer to \secref{chap:faq}{the FAQ section} or contact our support team through the GitHub repository or Matrix Support Room. Happy reviewing!
